---
title: "Developing Data Products Week-4 Project"
author: "Eswara S"
date: "March 13, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Detail


As part of the Coursera Data Projects course project, there was a requirement to create a Shiny web application and then present a pitch presentation.

The purpose is to write a structured presentation. I will do that by taking you through my Shiny app and why I did, what I did.

## Plot Hodgepodge

I gave a try to make Hodgepodge by taking inputs from user


Plot a Hodgepodge by inputting,

1. Sequence length 

2. Knot length

## Slide with server.R code

```{r, echo = TRUE}
MyPlot <- function(n)
{
   x <- seq(0,4*pi, length = 100); y <- sin(x) + rnorm( n, sd=0.3)
   knots <- seq(0, 8*pi, length = 100)
   splineTerms <- sapply(knots, function(knot)(x > knot) * (x - knot))
   xMat <- cbind(1,x,splineTerms)
   yhat <- predict(lm(y ~ xMat - 1))
   plot(x, y, frame = FALSE, pch = 21, bg = "blue", cex = 2)
   lines(x, yhat, col = "red", lwd = 2)
}
```

## Slide with Plot
```{r, echo=TRUE}
MyPlot(100)
```
